Empirical normative theories

### 2020-08-03 simple.tex
Attempts proofs correspondence c and def

Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$. (The striked through $\phi$ in superscript is there to suggest that, intuitively, $\args$ argue against $\phi$, from the point of view of $i$.)

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	$\dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.

	First (from left to right), $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)}$. 
	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, and $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$. Also, picking any $\ard \in \dargs$, we see that for some $\ar_1 \in \args$, $\ard \dbeats \ar_1 \gbeats \ar_0$.

	Second (from right to left), $\dargs \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incorrect.}. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{proof}

>>>>

Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$. (The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.)

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	$\dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$. Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$.

	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0)$, define $\dargs = \dbeatsinv(\args)$, and let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$. 
	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$. Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.

	Second (from right to left), $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incomplete, should mention injectivity.}. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{proof}

\begin{proof}[Alternative proof]
	Given $\args, \dargs, \ar$ such that $\emptyset ≠ \args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar)$:
	\begin{equation}
		\dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
	\end{equation}

	LHS equiv $\ard \in \dargs ⇔ \exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1$.
	Using $\args \subseteq \gbeatsinv(\ar)$, it is also equivalent to: $\ard \in \dargs ⇔ \exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1 \gbeats \ar$.

	RHS equiv $\ard \in \dargs ⇒ \exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar$.

	LHS implies RHS. Obvious.

	RHS implies LHS. First, $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$ (by RHS), and $\ard \in \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\ard) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\dargs) \suchthat \ard \dbeats \ar_1 ⇔ \ard \in \dbeatsinv(\args)$.

	Second, $\exists \ar_1 \in \args \suchthat \ard \dbeats \ar_1 ⇒ \ard \in \dargs$: it follows from $\args \subseteq \dbeats(\dargs)$ and injectivity: $\ar_1 \in \args$ thus $\ar_1 \in {\dbeats}(\dargs)$ thus $\exists \ar_2 \in \dargs \suchthat \ar_2 \dbeats \ar_1$, and $\ar_2 = \ard$ by injectivity, thus $\ard \in \dargs$.

	Finally, prove that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$.
	\commentOC{This equivalence is true, but the proof above might be insufficient: it only proves that RHS ⇒ LHS when $\args$ is chosen as defined, but it could be that sometimes $\args$ can be chosen differently, so that $\dbeatsinv(\args) = \dargs$ but $\args ≠ {\dbeats}(\dargs)$.}
\end{proof}

\begin{proof}[More promising]
	$\forall \dargs \subseteq \allargs$:
	\begin{equation}
		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
	\end{equation}

	LHS implies RHS. Prove that $\emptyset ≠ \dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$. $\args \subseteq \gbeatsinv(\ar)$, thus, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$. Also, $\args ≠ \emptyset$, thus $\dbeatsinv(\args) ≠ \emptyset$, as mandated by $\dbeats$, by definition of empirical theories.

	RHS implies LHS. Define $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar)$ and prove that $\args ≠ \emptyset$ and $\dbeatsinv(\args) = \dargs$.

	First, $\dargs \subseteq \dbeatsinv(\args)$. That is because $\dbeatsinv(\gbeatsinv(\ar)) = \dbeatsinv(\args)$. This can be seen by: $\ard \in \dbeatsinv(\gbeatsinv(\ar)) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\ard) ⇔ \exists \ar_1 \in \gbeatsinv(\ar) \cap {\dbeats}(\dargs) \suchthat \ard \dbeats \ar_1 ⇔ \ard \in \dbeatsinv(\args)$.

	Second, $\dbeatsinv(\args) \subseteq \dargs$. That is because $\dbeatsinv(\args) \subseteq \dbeatsinv({\dbeats}(\dargs)) \subseteq \dargs$, by injectivity of $\dbeats$.

	RHS implies LHS (alt). RHS implies $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$, which implies that $\dbeatsinv({\dbeats}(\dargs)) = \dargs$, by injectivity of $\dbeats$, and $\dbeatsinv({\dbeats}(\dargs)) = \dbeatsinv({\dbeats}(\dargs) \cap \gbeatsinv(\ar))$. 
	Therefore, $\dargs = \dbeatsinv({\dbeats}(\dargs)) = \dbeatsinv({\dbeats}(\dargs) \cap \gbeatsinv(\ar)) = \dbeatsinv(\args)$.
\end{proof}
